---
title: clumpr
output: 
  github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![Travis Build Status](https://travis-ci.com/UBESP-DCTV/clumpr.svg?token=wGyFLep97LHjNKfPGjkg&branch=structures)](https://travis-ci.org/UBESP-DCTV/clumpr)
[![Codecov Status](https://codecov.io/gh/UBESP-DCTV/clumpr/branch/structures/graph/badge.svg?token=IY02gbLUth)](https://codecov.io/gh/UBESP-DCTV/clumpr)
[![Build status](https://ci.appveyor.com/api/projects/status/2q6ylqbu14cu43am?svg=true)](https://ci.appveyor.com/project/CorradoLanera/clumpr)
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![CRAN status](https://www.r-pkg.org/badges/version/clumpr)](https://cran.r-project.org/package=clumpr)

**C**urrent transp**L**ant s**U**rplus **M**anagement **P**rotocol in **R**

Last update: `r Sys.Date()`

## Description

The `clumpr` package aims to provide a toolbox of function for model,
validate and visualize dynamics assessed by the "Protocollo Nazionale per la
Gestione delle Eccedenze di Tutti i Programmi di Trapianto" in Italy.

The first implementation is focused on the lung-transplant centers
management.



## Example

This is a basic example which shows you how it works:


```{r}
library(clumpr)

# setup centers and regions
pavia   <- center('Pavia',   'Lombardia', offered = 11, p_accept = 0.8)
bergamo <- center('Bergamo', 'Lombardia', offered =  7, p_accept = 0.5)
milano  <- center('Milano',  'Lombardia', offered =  3)

lombardia <- region(set_centers(pavia, bergamo, milano), default_p = 0.2)

# show data
lombardia
get_centers(lombardia)

# setup macroregions
padova <- center('Padova', 'Veneto', 10, 0.9)
veneto <- region(set_centers(padova))

nitp <- macroregion('NITp', set_regions(lombardia, veneto),
  initial_strip = c('lombardia',  'lombardia', 'veneto'))

# show data
nitp
get_regions(nitp)
get_centers(nitp)

# add another region and setup a macroarea
torino   <- center('Torino', 'Piemonte', 7, 0.6)
piemonte <- region(set_centers(torino))

nord <- macroarea('Nord',
  macroregions = set_macroregions(piemonte, nitp)
)

nord
get_macroregions(nord)
get_regions(nord)
get_centers(nord)

roma   <- center('Roma', 'Lazio', 10, 0.9)
lazio  <- region(set_centers(roma))

sud <- macroarea('Sud',
  macroregions = set_macroregions(lazio)
)

italy <- state('Italy', set_macroareas(nord, sud))
italy

get_macroareas(italy)
get_macroregions(italy)
get_regions(italy)
get_centers(italy)

# TODO
```



## Installation

You can install clumpr from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("UBESP-DCTV/clumpr")
```



## Bug reports
If you encounter a bug, please file a
[reprex](https://github.com/tidyverse/reprex) (minimal reproducible example)
to <https://github.com/UBESP-DCTV/clumpr/issues>


## Code of conduct
Please note that this project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this
project you agree to abide by its terms.

## References

**Protocollo Nazionale per la Gestione delle Eccedenze di Tutti i Programmi
di Trapianto** ([pdf](http://www.policlinico.mi.it/AMM/nitp/area_operatore/linee_guida/03/ProtocolloNazionaleGestioneEccedenzeCNTO140804.pdf))
