---
title: clumpr
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![Travis Build Status](https://travis-ci.org/UBESP-DCTV/clumpr.svg?branch=develop)](https://travis-ci.org/UBESP-DCTV/clumpr)

[![CRAN Status Badge](https://www.r-pkg.org/badges/version/clumpr.svg)](http://cran.R-project.org/)

[![Coverage status](https://codecov.io/gh/UBESP-DCTV/clumpr/branch/develop/graph/badge.svg)](https://codecov.io/github/UBESP-DCTV/clumpr?branch=develop)

**C**urrent transp**L**ant s**U**rplus **M**anagement **P**rotocol in **R**

Last update: `r Sys.Date()`

## Description

The `clumpr` package aims is to provide a toolbox of function for model,
validate and visualize dynamics assessed by the "Protocollo Nazionale per la
Gestione delle Eccedenze di Tutti i Programmi di Trapianto" in Italy.

The first implementation is focused on the lung-transplant centers
management.



## Example

This is a basic example which shows you how it works:


```{r}
# TODO
```



## Installation

You can install viper from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("UBESP-DCTV/clumpr")
```



## Bug reports
If you encounter a bug, please file a
[reprex](https://github.com/tidyverse/reprex) (minimal reproducible example)
to <https://github.com/UBESP-DCTV/clumpr/issues>



## References

**Protocollo Nazionale per la Gestione delle Eccedenze di Tutti i Programmi
di Trapianto** ([pdf](http://www.policlinico.mi.it/AMM/nitp/area_operatore/linee_guida/03/ProtocolloNazionaleGestioneEccedenzeCNTO140804.pdf))
