---
title: viper
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

**V**al**I**dazione **P**rotocollo **E**ccedenze t**R**apianto

Last update: `r Sys.Date()`

## Description

The `viper` package aims is to provide a toolbox of function for model,
validate and visualize dynamics assessed by the "Protocollo Nazionale per la
Gestione delle Eccedenze di Tutti i Programmi di Trapianto" in Italy.

The first implementation is focused on the lung-transplant centers
management.



## Example

This is a basic example which shows you how it works:


```{r}
# TODO
```



## Installation

You can install viper from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("UBESP-DCTV/viper")
```



## Bug reports
If you encounter a bug, please file a
[reprex](https://github.com/tidyverse/reprex) (minimal reproducible example)
to <https://github.com/UBESP-DCTV/viper/issues>



## References

**Protocollo Nazionale per la Gestione delle Eccedenze di Tutti i Programmi
di Trapianto** ([pdf](http://www.policlinico.mi.it/AMM/nitp/area_operatore/linee_guida/03/ProtocolloNazionaleGestioneEccedenzeCNTO140804.pdf))
